Constructing Quotient Inductive-Inductive Types

### 2018-11-09 paper.tex
Add appendix url footnote

In the following table we summarize the operations which we define in
Sections \ref{sec:algebras}--\ref{sec:eliminator}. $\Gamma$ denotes a
signature. The full definitions of these operations are given in
Appendix A.

@@

The Agda formalisation has been checked using Agda 2.5.4. It is
available at
\url{https://bitbucket.org/akaposi/finitaryqiit/src/master/}, together
with a technical appendix. The Agda formalisation covers sections
\ref{sec:syntax}, \ref{sec:syntaxfunctions}, \ref{sec:algebras}, the
definition of homomorphisms from \ref{sec:recursor}, and also
\ref{sec:eliminator}, \ref{sec:definingcwf}, \ref{sec:cwfalg},
\ref{sec:initind}, and part of \ref{sec:cwfmodel}. The formalisation
also includes additional documentation concerning technicalities.

>>>>

In the following table we summarize the operations which we define in
Sections \ref{sec:algebras}--\ref{sec:eliminator}. $\Gamma$ denotes a
signature. The full definitions of these operations are given in
Appendix A\footnote{Available at \url{https://bitbucket.org/akaposi/finitaryqiit/raw/master/appendix.pdf}}.

@@

The Agda formalisation has been checked using Agda 2.5.4. It is
available at
\url{https://bitbucket.org/akaposi/finitaryqiit}, together
with a technical appendix. The Agda formalisation covers sections
\ref{sec:syntax}, \ref{sec:syntaxfunctions}, \ref{sec:algebras}, the
definition of homomorphisms from \ref{sec:recursor}, and also
\ref{sec:eliminator}, \ref{sec:definingcwf}, \ref{sec:cwfalg},
\ref{sec:initind}, and part of \ref{sec:cwfmodel}. The formalisation
also includes additional documentation concerning technicalities.
